---
title: "Data Transalation: Visitors in July/2020 in King County"
author: "Everly Ho"
date: "5/14/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
install.packages("tigris")
install.packages("sqldf")
install.packages("gsubfn")
install.packages("proto")
install.packages("RSQLite")
install.packages("ggplot2")
install.packages("rmarkdown")
library(tigris)
library(sqldf)
library(ggplot2)
library(rmarkdown)

setwd(dirname(rstudioapi::getSourceEditorContext()$path))

# Read in the revised origin data
dailyvisits <- readRDS('king_dailyvisits.Rdata')

theme_color <- c("#ef8498", "#00a4ec", "#3acec7", "#455abd", "#ffc83d", "#5c6ac4", "#bf9dee", "#ff8d4f","#4fc186", "#638fd4")

#5 CHART ONE STORY
  #1: BAR CHART ABOUT naics SUM VISIT IN JULY/2020 DESC ORDER
  #2: LINE CHART ABOUT VISIT BY DATE, 
        #1 LINE naics WITH THE MOST VISIT
        #2 AVG VIST
        #3 LINE naics WITH THE LEAST VISIT
  #3: naics WITH THE MOST VISIT, PIE (DONUT) CHART ABOUT BRAND SUM VISIT IN JULY/2020
        #NOTE: brands null mean "Smaller brands"
  #4: naics WITH THE MOST VISIT, BRAND LINE CHART ABOUT VISIT BY DATE
  #5: BRAND WITH THE MOST VISIT, BRAND LINE CHART ABOUT VISIT BY DATE

  
#chart 1
monthly_visit <- sqldf('SELECT naics_code, naics_title, SUM(visits_by_day) AS sum_visit 
            FROM dailyvisits 
            WHERE naics_title IS NOT NULL
            GROUP BY naics_code, naics_title 
            ORDER BY 3 desc')


data1 <- sqldf('SELECT naics_title, sum_visit FROM monthly_visit LIMIT 10')

data1$fraction = data1$sum_visit / sum(data1$sum_visit)
data1$ymax = cumsum(data1$fraction)
data1$ymin = c(0, head(data1$ymax, n=-1))
data1$labelPosition <- (data1$ymax + data1$ymin) / 2
data1$label <- data1$sum_visit

chart1 <- ggplot(data1, aes(ymax=ymax, ymin=ymin, xmax=4, xmin=3, fill=naics_title)) +
 # geom_bar(stat = "identity", color = "white") +
  geom_rect() +
  geom_label(x=3.5, aes(y=labelPosition, label=label), size=4, color = "#333333") +
  scale_fill_manual(values = theme_color) +
  coord_polar(theta="y") + 
  xlim(c(2, 4)) +
  theme_void() +
  labs(fill = "Industries")  +
  theme(legend.title = element_text(colour="#333333", size=12, face="bold"))


#chart 2
avg_daily_visit <- sqldf('SELECT date, "Average visit" as key, ROUND(AVG(visits_by_day),0) AS daily_visit 
            FROM dailyvisits 
            WHERE naics_title IS NOT NULL
            GROUP BY date
            ORDER BY 1')

most_naics_daily_visit <- sqldf('SELECT date, naics_title as key, SUM(visits_by_day) AS daily_visit 
                                FROM dailyvisits 
                                WHERE naics_code in (SELECT naics_code FROM monthly_visit LIMIT 3)
                                GROUP BY date, naics_code, naics_title
                                ORDER BY 1')

data2 <- sqldf('SELECT * FROM most_naics_daily_visit
                UNION
                SELECT * FROM avg_daily_visit')

chart2 <- ggplot(data2, aes(x=date, y=daily_visit, group=key, color=key)) +
  geom_line(size=0.5) +
  geom_point(size=1) +
  scale_color_discrete(name = "Industries") +
  xlab("Date") +
  ylab("Visit") +
  theme_linedraw() +
  theme_light() +
  scale_x_date(breaks = data2$date) + 
  theme(axis.text.x = element_text(angle = 90)) +
  theme(legend.position="bottom") +
  theme(legend.title = element_text(colour="#333333", size=12, face="bold")) +
  theme(legend.text = element_text(colour="#333333", size=6))


#chart 3
data3 <- sqldf('SELECT CASE WHEN brands="" THEN "Other smaller brands" ELSE brands END AS brands,
                              SUM(visits_by_day) AS sum_visit 
                              FROM dailyvisits 
                              WHERE naics_code IN (SELECT naics_code FROM monthly_visit LIMIT 1)
                              GROUP BY 1
                              ORDER BY 2 desc')


data3$fraction = data3$sum_visit / sum(data3$sum_visit)
data3$ymax = cumsum(data3$fraction)
data3$ymin = c(0, head(data3$ymax, n=-1))
data3$labelPosition <- (data3$ymax + data3$ymin) / 2
data3$label <- data3$sum_visit

chart3 <- ggplot(data3, aes(ymax=ymax, ymin=ymin, xmax=4, xmin=3, fill=brands)) +
  # geom_bar(stat = "identity", color = "white") +
  geom_rect() +
  geom_label(x=3.5, aes(y=labelPosition, label=label), size=4, color = "#333333") +
  scale_fill_brewer(palette=2) +
  coord_polar(theta="y") + 
  xlim(c(2, 4)) +
  theme_void() +
  labs(fill = "Brands") +
  theme(plot.title = element_text(face ="bold", color="#333333", size=12)) +
  theme(legend.title = element_text(colour="#333333", size=12, face="bold"))


#chart 4
data4 <- sqldf('SELECT date, CASE WHEN brands="" THEN "Other smaller brands" ELSE brands END AS key, visits_by_day 
                FROM dailyvisits 
                WHERE naics_code IN (SELECT naics_code FROM monthly_visit LIMIT 1)
                ORDER BY date')

chart4 <- ggplot(data4, aes(x=date, y=visits_by_day, group=key, color=key)) +
  geom_line(size=0.5) +
  geom_point(size=1) +
  scale_color_discrete(name = "Brands") +
  xlab("Date") +
  ylab("Visit") +
  theme_linedraw() +
  theme_light() +
  scale_x_date(breaks = data4$date) + 
  theme(axis.text.x = element_text(angle = 90)) +
  theme(legend.position="bottom") +
  theme(legend.title = element_text(colour="#333333", size=12, face="bold"))

#chart 5
data5 <- sqldf('SELECT date, SUM(visits_by_day) AS sum_visit 
                FROM dailyvisits 
                WHERE naics_title IS NOT NULL
                GROUP BY date')

chart5 <- ggplot(data5, aes(x=date, y=sum_visit)) +
  geom_line(size=0.5, color="#ff8d4f") +
  geom_point(size=1, color="#ff8d4f") +
  xlab("Date") +
  ylab("Visit") +
  theme_linedraw() +
  theme_light() + 
  scale_x_date(breaks = data5$date) + 
  theme(axis.text.x = element_text(angle = 90))

top_naics_title <- monthly_visit$naics_title[1]
```

## Introduction

After examining **king_dailyvisits** data, there are some interesting point about number of visit changing daily. These interesting point are visualized as follows:


## Total visit daily in July/2020

```{r chart1, echo=FALSE, out.width="80%"}
chart5
```

As we can see, total visit drop to its lowest at the weekend and tends to increase gradually towards the end of the month.

## Top 10 Industries have the most visit in July/2020

```{r chart2, echo=FALSE, out.width="80%"}
chart1
```

The chart show Industries with the most visit, these are essential services Like accommodation, food and health.

## Top 3 Industries and average daily visit data in July/2020

```{r chart3, echo=FALSE, out.width="80%"}
chart2
```

Like total visit data, number of visits of top 3 Industries tends to be in its peak at Friday and drop to its lowest at the weekend. But, Park's visit data is different, its highest is in the weekend and tends to be lowest at Friday.

## Total visit of `r top_naics_title` brands in July/2020

```{r chart4, echo=FALSE, out.width="80%"}
chart3
```

In the most visit industry data, `r top_naics_title`, We can see that most people support smaller brands.

## Daily visit of `r top_naics_title` brands in July/2020

```{r chart5, echo=FALSE, out.width="80%"}
chart4
```

Number of visits of big brands is pretty stable, unlike smaller brands which difference between the highest and the lowest is too large.